\rm Weak compactness of probability measures

### 2018-07-05 manuscript-3.tex
Changing the duals to asts.

\begin{theo}[Measures as a dual space]\label{charact}
With the above notations the linear mapping
\begin{equation*}
I\colon ba(\mathcal A) \to L^0_b(\mathcal A)^\prime, \quad \mu\mapsto I\mu \coloneqq%F_\mu\coloneqq
 \left(f\mapsto\int f\mathrm{d}\mu\right)
\end{equation*}
is an algebraic isomorphism and we have \(\left\lVert I\mu \right\rVert_{L^0_b(\mathcal A)^\ast} = \left\lVert \mu \right\rVert_{BV}\). In particular \(\left\lVert \cdot \right\rVert_{BV}\) is a norm and \(ba(\mathcal A)\) is complete with respect to it.
%isometric isomorphism.
 Further the inverse \(I^{-1}\) is given by
\[F\mapsto \Big( A\mapsto F(\chi_A)\Big).\]
For a measure \(\mu\in ba(\mathcal A)\) the following three statements are equivalent:
%is countably additive if and only if one of the two following equivalent properties holds:
\begin{enumerate}
\item \(\mu\) is countably additive.
\item \(I\mu\) fulfills the monotone convergence theorem.
\item \(I\mu\) fulfills the dominated convergence theorem.
\end{enumerate}
\end{theo}
\begin{proof}
The previous theorem directly implies that \(I\) is a well defined linear contraction, i.e. %It is clear that \(I\) is linear, bijective and well defined and %further the estimate \eqref{e1} yields %Further we have
%\[\mu(f)\le \int \left\lvert f \right\rvert\mathrm{d}\!\left\lvert \mu \right\rvert \le \left\lVert f \right\rVert_{L^0_b(\mathcal A)} \left\lVert \mu \right\rVert_{ba(\mathcal A)}, \]
%and therefore
\(\left\lVert I\mu \right\rVert\le \left\lVert \mu \right\rVert\). To see that the mapping is an isometry we take a finite collection \(\mathcal E\) of disjoint measurable sets. Then we get
\[\left\lVert I\mu \right\rVert_{L^0_b(\mathcal A)^\prime} \ge \int\limits \sum\limits_{E\in\mathcal E} \operatorname{sign}(\mu(E)) \chi_E\mathrm d\mu = \sum\limits_{E\in\mathcal E} \left\lvert \mu(E) \right\rvert. \]
%By choosing \(f\coloneqq \chi_{A_+} - \chi_{A_-}\), where \(A_+\) and \(A_-\) are the sets out of the Hahn-Jordan decomposition of \(\mu\) we get
%\[\mu(f) = \mu(A_+) - \mu(A_-) = \left\lVert \mu \right\rVert\]
By taking the supremum over all those collections \(\mathcal E\) we get \(\left\lVert I\mu \right\rVert = \left\lVert \mu \right\rVert\). Further the bijectivity follows from the fact \(I\circ I^{-1} =\operatorname{id}_{L^0_b(\mathcal A)^\prime}, I^{-1}\circ I = \operatorname{id}_{ba(\mathcal A)}\).  % \(I\mu_F = F\) and \(\mu_\)

@@

\begin{theo}[Dual of \(L^\infty(\mu)\)]
Let \(\mu\in ba(\mathcal A)\) and let \( ba(\mu)\subseteq ba(\mathcal A)\) be the subspace of measure that are absolutely continuous wrt \(\mu\). Then we have 
\[ ba(\mu) \cong L^\infty(\mu)^\prime \]
isometrically in the canonical way.
\end{theo}
\begin{proof}
Let \([f]_\mu\) denote the \(\mu\) ‚a.e. equivalence‘ class of \(f\in L^0_b(\mathcal A)\), then 
\[\iota:L^0_b(\mathcal A) \to L^\infty(\mu), \quad f\mapsto[f]_\mu\]
is surjective and further we have
\begin{equation}\label{e3}
\left\lVert [f]_\mu \right\rVert_{L^\infty(\mathcal A)} = \inf_{g\in [f]_\mu} \left\lVert g \right\rVert_\infty .
\end{equation}
Therefore the dual operator
\[\iota^\prime\colon L^\infty(\mu)^\prime \to L^0_b(\mathcal A)^\prime \cong ba(\mathcal A)\]
is injective and because of \eqref{e3} it is isometric since it implies \(\iota(B_1) = B_1\) where \(B_1\) denotes the unit ball in the respective spaces. %Indeed we have
%\[\left\lvert \iota^\prime F(f) \right\rvert = \left\lvert F[f]_\mu \right\rvert \le \left\lVert F \right\rVert_{L^\infty(\mu)^\prime} \cdot \left\lVert [f]_\mu \right\rVert_{L^\infty(\mu)} \le \left\lVert F \right\rVert_{L^\infty(\mu)^\prime}\cdot\left\lVert f \right\rVert_\infty\]
%and with Hahn Banach we get
%\[\left\lVert F \right\rVert_{L^\infty(\mu)^\prime} = F[f]_{\mu} = \lim \iota^\prime Fg_n\]
%with \((g_n)\subseteq [f]_\mu\) with \(\left\lVert g_n \right\rVert\to 1\).
Further the closed range theorem implies
\[\operatorname{ran}(\iota^\prime) = \operatorname{ker}(\iota)^\perp = \left\{ F\in L^0_b(\mathcal A)^\prime\mid F(f) = 0 \text{ for all } %f \text{ s.t. }
 f = 0 \text{ \(\mu\) a.e.}\right\} \cong ba(\mu).\]
\end{proof}

\begin{emp}[Characterisation of other dual spaces]
A similar approach can be used to characterise the dual spaces of other normed spaces of bounded measurable functions, for example the dual of all bounded continuous functions \(\mathcal C_b(X)\) if we are dealing with a topological space \(X\). If we denote the Borel algebra by \(\mathcal B\) we get
\[\iota\colon\mathcal C_b(X) \hookrightarrow L^0_b(\mathcal B) \]
isometrically and therefore 
\[\iota^\ast\colon ba(\mathcal B) \cong L^0_b(\mathcal B)^\ast \to\!\!\!\!\!\to \mathcal C_b(X)^\prime, \quad \mu\mapsto \big( f\mapsto \mu(f)\big)\]
is surjective, but not necessarily isometric and not injective if \(\mathcal C_b(X)\subsetneq L^0_b(\mathcal B)\). Of course one could argue that we then have \(\mathcal C_b(X)^\ast\cong ba(\mathcal B)/\operatorname{ker}(\iota^\ast)\) but that characterisation is very implicit.
 However one can characterise that quotient space is some cases -- usually under certain regularity condition on the space -- as a 
 %show in some cases -- if the topological space \(X\) is regular enough -- that the restriction of \(\iota^\prime\) to 
 subspace of \(ba(\mathcal A)\). For detail on this we refer to the chapter about positive functionals in \cite{rudin2006real}. % is injective and also surjective but 
%Usually one also has to work with other spaces of bounded continuous functions like the continuous functions vanishing at infinity. Since those results are somewhat technical to prove (but not necessarily hard) they will not be presented here. \todo{elaborate and cite this!}% to reconstruct the measure \(\mu(A) = \mu(\chi_A)\) from the values \(\mu(f)\) for \(f\in\mathcal C_b(X)\).
\end{emp}

>>>>

\begin{theo}[Measures as a dual space]\label{charact}
With the above notations the linear mapping
\begin{equation*}
I\colon ba(\mathcal A) \to L^0_b(\mathcal A)^\ast, \quad \mu\mapsto I\mu \coloneqq%F_\mu\coloneqq
 \left(f\mapsto\int f\mathrm{d}\mu\right)
\end{equation*}
is an algebraic isomorphism and we have \(\left\lVert I\mu \right\rVert_{L^0_b(\mathcal A)^\ast} = \left\lVert \mu \right\rVert_{BV}\). In particular \(\left\lVert \cdot \right\rVert_{BV}\) is a norm and \(ba(\mathcal A)\) is complete with respect to it.
%isometric isomorphism.
 Further the inverse \(I^{-1}\) is given by
\[F\mapsto \Big( A\mapsto F(\chi_A)\Big).\]
For a measure \(\mu\in ba(\mathcal A)\) the following three statements are equivalent:
%is countably additive if and only if one of the two following equivalent properties holds:
\begin{enumerate}
\item \(\mu\) is countably additive.
\item \(I\mu\) fulfills the monotone convergence theorem.
\item \(I\mu\) fulfills the dominated convergence theorem.
\end{enumerate}
\end{theo}
\begin{proof}
The previous theorem directly implies that \(I\) is a well defined linear contraction, i.e. %It is clear that \(I\) is linear, bijective and well defined and %further the estimate \eqref{e1} yields %Further we have
%\[\mu(f)\le \int \left\lvert f \right\rvert\mathrm{d}\!\left\lvert \mu \right\rvert \le \left\lVert f \right\rVert_{L^0_b(\mathcal A)} \left\lVert \mu \right\rVert_{ba(\mathcal A)}, \]
%and therefore
\(\left\lVert I\mu \right\rVert\le \left\lVert \mu \right\rVert\). To see that the mapping is an isometry we take a finite collection \(\mathcal E\) of disjoint measurable sets. Then we get
\[\left\lVert I\mu \right\rVert_{L^0_b(\mathcal A)^\ast} \ge \int\limits \sum\limits_{E\in\mathcal E} \operatorname{sign}(\mu(E)) \chi_E\mathrm d\mu = \sum\limits_{E\in\mathcal E} \left\lvert \mu(E) \right\rvert. \]
%By choosing \(f\coloneqq \chi_{A_+} - \chi_{A_-}\), where \(A_+\) and \(A_-\) are the sets out of the Hahn-Jordan decomposition of \(\mu\) we get
%\[\mu(f) = \mu(A_+) - \mu(A_-) = \left\lVert \mu \right\rVert\]
By taking the supremum over all those collections \(\mathcal E\) we get \(\left\lVert I\mu \right\rVert = \left\lVert \mu \right\rVert\). Further the bijectivity follows from the fact \(I\circ I^{-1} =\operatorname{id}_{L^0_b(\mathcal A)^\ast}, I^{-1}\circ I = \operatorname{id}_{ba(\mathcal A)}\).  % \(I\mu_F = F\) and \(\mu_\)

@@

\begin{theo}[Dual of \(L^\infty(\mu)\)]
Let \(\mu\in ba(\mathcal A)\) and let \( ba(\mu)\subseteq ba(\mathcal A)\) be the subspace of measure that are absolutely continuous wrt \(\mu\). Then we have 
\[ ba(\mu) \cong L^\infty(\mu)^\ast \]
isometrically in the canonical way.
\end{theo}
\begin{proof}
Let \([f]_\mu\) denote the \(\mu\) ‚a.e. equivalence‘ class of \(f\in L^0_b(\mathcal A)\), then 
\[\iota:L^0_b(\mathcal A) \to L^\infty(\mu), \quad f\mapsto[f]_\mu\]
is surjective and further we have
\begin{equation}\label{e3}
\left\lVert [f]_\mu \right\rVert_{L^\infty(\mathcal A)} = \inf_{g\in [f]_\mu} \left\lVert g \right\rVert_\infty .
\end{equation}
Therefore the dual operator
\[\iota^\ast\colon L^\infty(\mu)^\ast \to L^0_b(\mathcal A)^\ast \cong ba(\mathcal A)\]
is injective and because of \eqref{e3} it is isometric since it implies \(\iota(B_1) = B_1\) where \(B_1\) denotes the unit ball in the respective spaces. %Indeed we have
%\[\left\lvert \iota^\prime F(f) \right\rvert = \left\lvert F[f]_\mu \right\rvert \le \left\lVert F \right\rVert_{L^\infty(\mu)^\prime} \cdot \left\lVert [f]_\mu \right\rVert_{L^\infty(\mu)} \le \left\lVert F \right\rVert_{L^\infty(\mu)^\prime}\cdot\left\lVert f \right\rVert_\infty\]
%and with Hahn Banach we get
%\[\left\lVert F \right\rVert_{L^\infty(\mu)^\prime} = F[f]_{\mu} = \lim \iota^\prime Fg_n\]
%with \((g_n)\subseteq [f]_\mu\) with \(\left\lVert g_n \right\rVert\to 1\).
Further the closed range theorem implies
\[\operatorname{ran}(\iota^\ast) = \operatorname{ker}(\iota)^\perp = \left\{ F\in L^0_b(\mathcal A)^\ast\mid F(f) = 0 \text{ for all } %f \text{ s.t. }
 f = 0 \text{ \(\mu\) a.e.}\right\} \cong ba(\mu).\]
\end{proof}

\begin{emp}[Characterisation of other dual spaces]
A similar approach can be used to characterise the dual spaces of other normed spaces of bounded measurable functions, for example the dual of all bounded continuous functions \(\mathcal C_b(X)\) if we are dealing with a topological space \(X\). If we denote the Borel algebra by \(\mathcal B\) we get
\[\iota\colon\mathcal C_b(X) \hookrightarrow L^0_b(\mathcal B) \]
isometrically and therefore 
\[\iota^\ast\colon ba(\mathcal B) \cong L^0_b(\mathcal B)^\ast \to\!\!\!\!\!\to \mathcal C_b(X)^\ast, \quad \mu\mapsto \big( f\mapsto \mu(f)\big)\]
is surjective, but not necessarily isometric and not injective if \(\mathcal C_b(X)\subsetneq L^0_b(\mathcal B)\). Of course one could argue that we then have \(\mathcal C_b(X)^\ast\cong ba(\mathcal B)/\operatorname{ker}(\iota^\ast)\) but that characterisation is very implicit.
 However one can characterise that quotient space is some cases -- usually under certain regularity condition on the space -- as a 
 %show in some cases -- if the topological space \(X\) is regular enough -- that the restriction of \(\iota^\prime\) to 
 subspace of \(ba(\mathcal A)\). For detail on this we refer to the chapter about positive functionals in \cite{rudin2006real}. % is injective and also surjective but 
%Usually one also has to work with other spaces of bounded continuous functions like the continuous functions vanishing at infinity. Since those results are somewhat technical to prove (but not necessarily hard) they will not be presented here. \todo{elaborate and cite this!}% to reconstruct the measure \(\mu(A) = \mu(\chi_A)\) from the values \(\mu(f)\) for \(f\in\mathcal C_b(X)\).
\end{emp}
